A General and Parallel Platform for Mining Co-Movement Patterns over Large-scale Trajectories

### 2016-10-28 Camera-Ready/sec4_baseline.tex
Camera-Ready
Ohohoho

\begin{figure*} [t]
\center
\includegraphics[width=0.85\textwidth]{trm.eps}
    \vspace{-0.5em}
\caption{Workflow of Temporal Replication and Parallel Mining (TRPM). (a) and (b) correspond to the first mapreduce stage which clusters objects in each snapshot.  (c) and (d) correspond to the second mapreduce stage, which uses TRPM to detect GCMPs in parallel.}
\vspace{-0.5em}
\label{fig:trm}
\end{figure*}

%\vspace{-3mm}
\section{Baseline: Temporal Replication and Parallel Mining}
\label{sec:trm}
In this section, we propose a baseline solution that resorts to MapReduce as a general, parallel and scalable paradigm for GCMP mining. The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}. There are two stages of mapreduce jobs connected in a pipeline manner. The first stage deals with spatial clustering of objects in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining phase. In particular, for the first stage, the timestamp is treated as the key in the map phase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phase. Finally, the reducers output clusters of objects in each snapshot, represented by a list of key-value pairs $\langle t, S_t  \rangle$, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.

@@

\begin{proof}
\vspace{-0.5em}
Given a valid pattern $P$, we can always find at least one valid subsequence of $P.T$ that is also valid. Let $T'$ denote the valid subsequence of $P.T$ with the minimum length. In the worst case, $T'=P.T$. We define $\range(T)=\max(T) - \min(T) +1$ and prove the theorem by showing that $\range(T') \leq \eta$.
Since $T'$ can be written as a sequence of L-consecutive segments interleaved by gaps: $l_1,g_1,\ldots,l_{n-1}$, $g_{n-1},l_n$ ($n \geq 1$),
where $l_i$ is a segment and $g_i$ is a gap. Then, $\range(T')$
is calculated as $\Sigma_{i=1}^{i=n}|l_i| + \Sigma_{i=1}^{i=n-1} |g_i|$. Since $T'$
is valid, then $\Sigma_{i=1}^{i=n}|l_i| \geq K$. As $T'$ is minimum, if we remove the 
last $l_n$, the resulting sequence should not be valid. Let $K' = \Sigma_{i=1}^{i=n-1}|l_i|$, which
is the size of the first $(n-1)$ segments of $T'$. Then, $K' \leq K-1$.
Note that every $|l_i| \geq L$, thus $n \leq \lceil \frac{K'}{L} \rceil \leq \lceil \frac{K}{L} \rceil $. By
using the fact that every $|g_i| \leq G-1$, we achieve $\Sigma_{i=1}^{i=n-1} |g_i| \leq (n-1)(G-1)
\leq (\lceil \frac{K}{L} \rceil -1)(G-1)$. Next, we consider the difference between $K$ and $K'$, denoted by
$\Delta = K- K'$. To ensure $T'$'s validity, $l_n$ must equal to $\min(L, \Delta)$.
Then, $\Sigma_{i=1}^{i=n}|l_i| = K' + l_n = K - \Delta + \min(L, \Delta) \leq K - 1 + L$. We finish showing $\range(T') \leq \eta$.  Therefore, for any valid sequence $T$, there is at least one valid subsequence with range no greater than $\eta$ and hence this pattern can be detected in a partition with $\eta$ snapshots.
\end{proof}

@@

\begin{algorithm}[h]
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\ForAll{clusters $s$ in snapshot $S_t$} 
\label{code:ls-init-start}
\If{$|s| \geq M$}
\State $C\leftarrow C\cup \{\langle s, t \rangle \}$
\EndIf
\EndFor
\label{code:ls-init-end}
\ForAll{$S_j \in \{S_{t+1},\ldots,S_{t+\eta-1}\}$} \label{code:ls-sweep-starts}
	\State $N \gets \{\}$
	\ForAll {$(c,s) \in C \times S_j$} \label{code:ls-join-start}
		\State {$c' \gets \langle c.O \cap s.O, c.T \cup \{j\} \rangle$} \label{code:ls-join}
		\If {$c'.T$ is valid} 
			\State output $c'$
		\ElsIf{$|c'.O| \geq M$}
			\State $N\leftarrow N\cup \{c'\}$ \label{code:ls-m-prun}	
		\EndIf
	\EndFor \label{code:ls-join-ends}
	\ForAll {$c \in C$}
		\If{$j-\max(c.T)\geq G$}\label{code:ls-g-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
			\State output $c$, if $c$ is a valid pattern
		\EndIf  \label{code:ls-g-prune-ends}
		\If{$c$'s first segment is less than $L$}\label{code:ls-l-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
		\EndIf\label{code:ls-l-prune-ends}
	\EndFor
	\State $C\leftarrow C\cup N$
\EndFor\label{code:ls-sweep-ends}
\State output valid patterns in  $C$  \label{code:ls-valid-check}
\end{algorithmic}
\end{algorithm}
\vspace{-1em}

@@

\begin{algorithm}[h]
\caption{Temporal Replication and Parallel Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+K+L-1$
\State {\textit{---Map Phase---}}
\label{code:trm-map-start}
\ForAll{snapshots $S_t$}
	\ForAll{$i \in 1...{\eta-1}$}
		\State emit key-value pair $\langle \max(t-i,0), S_t \rangle$ 
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {\textit{---Partition and Shuffle Phase---}}
\label{code:trm-par-start}
\ForAll{key-value pairs $\langle t, S \rangle$} 
\State group-by $t$ and emit a key-value pair $\langle t, \lambda_t\rangle$, where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
\EndFor
\label{code:trm-par-end}
\State {\textit{---Reduce Phase---}}
\label{code:trm-red-start}
\ForAll{key-value pairs $\langle t,\lambda_t \rangle$}
\State call line sweep mining for partition $\lambda_t$
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}
\vspace{-0.5em}
The complete picture of TRPM is summarized in Algorithm~\ref{algo:trm_overview}. We illustrate the  workflow of TRPM using Figure~\ref{fig:trm} (c) and (d) with pattern
parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+ K + L - 1 = 5$. Therefore, 
in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set when sweeping snapshot $S_i$.
Initially, $C_1$ contains 
%patterns with 
all object sets in 
%snapshot 
$S_1$.
%As we sweep the snapshots, the patterns in $C_i$ grow.
At snapshot $S_4$, the candidate
$\langle o_5,o_6 \rangle$ is removed because the gap between its latest timestamp (i.e., $2$)
and the next sweeping timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
Next, at snapshot $S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed
because its local consecutive segment $(4)$ has only $1$ element,
which violates the $L$-consecutive constraint.
Finally, $\langle o_3,o_4 \rangle$ is the valid pattern and is returned. Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness. If $\eta$ is set to be $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.

>>>>

\begin{figure*} [t]
\center
\includegraphics[width=0.8\textwidth]{trm.eps}
%\vspace{-0.5em}
\caption{Workflow of Temporal Replication and Parallel Mining (TRPM). (a) and (b) correspond to the first mapreduce stage which clusters objects in each snapshot.  (c) and (d) is the second mapreduce stage which uses TRPM to detect GCMPs.}
%\vspace{-0.5em}
\label{fig:trm}
\end{figure*}

\section{Baseline: Temporal Replication and Parallel Mining}
\label{sec:trm}
In this section, we propose a baseline solution that resorts to MapReduce as a general, parallel and scalable paradigm for GCMP mining. The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}. There are two stages of mapreduce jobs connected in a pipeline manner. The first stage deals with spatial clustering of objects in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining phase. In particular, for the first stage, the timestamp is treated as the key in the map phase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phase. Finally, the reducers output clusters of objects in each snapshot, represented by a list of key-value pairs $\langle t, S_t  \rangle$, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.

@@

\begin{proof}
Given a valid pattern $P$, we can always find at least one valid subsequence of $P.T$ that is also valid. Let $T'$ denote the valid subsequence of $P.T$ with the minimum length. In the worst case, $T'=P.T$. We define $\range(T)=\max(T) - \min(T) +1$ and prove the theorem by showing that $\range(T') \leq \eta$.
Since $T'$ can be written as a sequence of L-consecutive segments interleaved by gaps: $l_1,g_1,\ldots,l_{n-1}$, $g_{n-1},l_n$ ($n \geq 1$),
where $l_i$ is a segment and $g_i$ is a gap. Then, $\range(T')$
is calculated as $\Sigma_{i=1}^{i=n}|l_i| + \Sigma_{i=1}^{i=n-1} |g_i|$. Since $T'$
is valid, then $\Sigma_{i=1}^{i=n}|l_i| \geq K$. As $T'$ is minimum, if we remove the 
last $l_n$, the resulting sequence should not be valid. Let $K' = \Sigma_{i=1}^{i=n-1}|l_i|$, which
is the size of the first $(n-1)$ segments of $T'$. Then, $K' \leq K-1$.
Note that every $|l_i| \geq L$, thus $n \leq \lceil \frac{K'}{L} \rceil \leq \lceil \frac{K}{L} \rceil $. By
using the fact that every $|g_i| \leq G-1$, we achieve $\Sigma_{i=1}^{i=n-1} |g_i| \leq (n-1)(G-1)
\leq (\lceil \frac{K}{L} \rceil -1)(G-1)$. Next, we consider the difference between $K$ and $K'$, denoted by
$\Delta = K- K'$. To ensure $T'$'s validity, $l_n$ must equal to $\min(L, \Delta)$.
Then, $\Sigma_{i=1}^{i=n}|l_i| = K' + l_n = K - \Delta + \min(L, \Delta) \leq K - 1 + L$. We finish showing $\range(T') \leq \eta$.  Therefore, for any valid sequence $T$, there is at least one valid subsequence with range no greater than $\eta$ and hence this pattern can be detected in a partition with $\eta$ snapshots.
\end{proof}

@@

\begin{algorithm}[h]
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\ForAll{clusters $s$ in snapshot $S_t$} 
\label{code:ls-init-start}
\If{$|s| \geq M$}
\State $C\leftarrow C\cup \{\langle s, t \rangle \}$
\EndIf
\EndFor
\label{code:ls-init-end}
\ForAll{$S_j \in \{S_{t+1},\ldots,S_{t+\eta-1}\}$} \label{code:ls-sweep-starts}
	\State $N \gets \{\}$
	\ForAll {$(c,s) \in C \times S_j$} \label{code:ls-join-start}
		\State {$c' \gets \langle c.O \cap s.O, c.T \cup \{j\} \rangle$} \label{code:ls-join}
		\If {$c'.T$ is valid} 
			\State output $c'$
		\ElsIf{$|c'.O| \geq M$}
			\State $N\leftarrow N\cup \{c'\}$ \label{code:ls-m-prun}	
		\EndIf
	\EndFor \label{code:ls-join-ends}
	\ForAll {$c \in C$}
		\If{$j-\max(c.T)\geq G$}\label{code:ls-g-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
			\State output $c$, if $c$ is a valid pattern
		\EndIf  \label{code:ls-g-prune-ends}
		\If{$c$'s first segment is less than $L$}\label{code:ls-l-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
		\EndIf\label{code:ls-l-prune-ends}
	\EndFor
	\State $C\leftarrow C\cup N$
\EndFor\label{code:ls-sweep-ends}
\State output valid patterns in  $C$  \label{code:ls-valid-check}
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[h]
\caption{Temporal Replication and Parallel Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+K+L-1$
\State {\textit{---Map Phase---}}
\label{code:trm-map-start}
\ForAll{snapshots $S_t$}
	\ForAll{$i \in 1...{\eta-1}$}
		\State emit key-value pair $\langle \max(t-i,0), S_t \rangle$ 
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {\textit{---Partition and Shuffle Phase---}}
\label{code:trm-par-start}
\ForAll{key-value pairs $\langle t, S \rangle$} 
\State group-by $t$ and emit a key-value pair $\langle t, \lambda_t\rangle$, where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
\EndFor
\label{code:trm-par-end}
\State {\textit{---Reduce Phase---}}
\label{code:trm-red-start}
\ForAll{key-value pairs $\langle t,\lambda_t \rangle$}
\State call line sweep mining for partition $\lambda_t$
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

The complete picture of TRPM is shown in Algorithm~\ref{algo:trm_overview}. We illustrate the  workflow of TRPM using Figures~\ref{fig:trm} (c) and (d) with pattern
parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+ K + L - 1 = 5$. Therefore, 
in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
into a partition in the map phase. In Figure~\ref{fig:trm} (d), the line sweep
method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set when sweeping snapshot $S_i$.
Initially, $C_1$ contains 
%patterns with 
all object sets in 
%snapshot 
$S_1$.
%As we sweep the snapshots, the patterns in $C_i$ grow.
At snapshot 
$S_4$, the candidate
$\langle o_5,o_6 \rangle$ is removed because the gap between its latest timestamp (i.e., $2$)
and the next sweeping timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
Next, at snapshot 
$S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed
because its local consecutive segment $(4)$ has only $1$ element,
which violates the $L$-consecutive constraint.
Finally, $\langle o_3,o_4 \rangle$ is the valid pattern and is returned. 
Note that in this example, $\eta=5$ is the minimum setting that 
can guarantee correctness. If $\eta$ is set to be $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.

### 2016-10-28 Camera-Ready/sec5_spm.tex
Camera-Ready
Ohohoho

\begin{figure*}[t]
\centering
\includegraphics[width=0.85\textwidth]{spm.eps}
\vspace{-0.5em}
\caption{Star Partitioning and ApRiori Enumerator (SPARE). (a) Aggregated graph $G_A$ generated from Figure 1. (b) Five star partitions are generated from $G_A$. Star IDs are circled, vertexes and inverted lists are in the connected tables.
(c) Apriori Enumerator with various pruning techniques.}
\label{fig:star_partition}
\vspace{-0.5em}
\end{figure*}

@@

Before we introduce the Apriori Enumerator, we are interested to 
examine the issue of global vertex ordering.
% on the moving objects.
This is because assigning different IDs to the objects will result in 
different star partitioning results, which will eventually affect the workload 
balance among reducers. The job with the performance bottleneck is often known as a  \emph{straggler}~\cite{kwon2012skewtune,coppa2015data}. In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition. We use $\Gamma$ to denote the size of such straggler partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}. Clearly, a star partitioning with small $\Gamma$ is preferred. For example, Figure~\ref{fig:star-alt} gives two star partitioning results under 
different vertex ordering on the same graph. The top one has $\Gamma = 5$ while the bottom one has $\Gamma = 3$. Obviously, the bottom one with smaller $\Gamma$ is much more balanced.

\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{star-alt.eps}
\vspace{-0.5em}
\caption{Star partitioning with different vertex orderings.}
\vspace{-0.5em}
\label{fig:star-alt}
\end{figure}

@@

\begin{theorem}
\label{THM:SPM_LB}
Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be the value derived from a random vertex ordering. With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}
\begin{proof}
   \vspace{-0.5em}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
If $G_A$ is dense, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
\begin{theorem}
\label{THM:SPM_LB_INC}
Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
\end{theorem}
\begin{proof}
 \vspace{-0.5em}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
Hence, we can simply use object ID to determine the vertex ordering in our implementation.

@@

\begin{example}
Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a decomposable sequence
because one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
In contrast, $T_2$ is a decomposable sequence because the sequence itself is the maximal $2$-connected subsequence, which is also $2$-consecutive and with size no smaller than $4$.
\end{example}

@@

Our customized Apriori Enumerator is presented in Algorithm~\ref{algo:apriori_mining}. Initially, the edges (pairs of objects) in the star constitute the bottom level (Lines~\ref{code:init-start}-\ref{code:init-end}) and invalid candidates are excluded (Line~\ref{code:simp1}). An indicator \emph{level} is used to control the result size for candidate joins. During each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}), only candidates with object size equals to \emph{level} are generated (Line~\ref{code:join-start}). When two candidates $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Line~\ref{code:join}). To check the validity of the candidate, we calculate $\mathtt{sim}(c'.T)$. If its simplified sequence is empty, $c'$ is excluded from the next level (Line~\ref{code:simp2}). This ensures that all the candidates with $P.O\supseteq c'.O$ are pruned. If a candidate cannot generate any new candidate, then
it is directly reported (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+,pei2000closet} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}). If yes, we can  terminate the algorithm early and output the results.

@@

Compared with TRPM, the SPARE framework does not rely on snapshot replication to guarantee correctness. In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
\begin{theorem}[Pattern Uniqueness]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
\end{theorem}
\begin{proof} 
\vspace{-0.5em}
We prove by contradiction. Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set. Note that the center vertex of the star is associated with the minimum id. Let $o_i$ and $o_j$ be the center vertexes of the two partitions and we have $o_i=o_j$. However, $P_i$ and $P_j$ are from different stars, meaning their center vertexes are different (i.e., $o_i\neq o_j$), leading to a contradiction. 
\vspace{-0.5em}
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}  
\vspace{-0.5em}
See Appendix~\ref{apx:spm_correct}.
\vspace{-0.5em}
\end{proof}

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\textwidth]{spm.eps}
%\vspace{-0.5em}
\caption{Star Partitioning and ApRiori Enumerator (SPARE). (a) Aggregated graph $G_A$ generated from Figure 1. (b) Five star partitions are generated from $G_A$. Star IDs are circled, vertexes and inverted lists are in the connected tables.
(c) Apriori Enumerator with various pruning techniques.}
\label{fig:star_partition}
%\vspace{-0.5em}
\end{figure*}

@@

Before we introduce the Apriori Enumerator, we are interested to 
examine the issue of global vertex ordering.
% on the moving objects.
This is because assigning different IDs to the objects will result in 
different star partitioning results, which will eventually affect the workload 
balance among reducers. The job with the performance bottleneck is often known as a  \emph{straggler}~\cite{kwon2012skewtune}. In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition. We use $\Gamma$ to denote the size of such straggler partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}. Clearly, a star partitioning with small $\Gamma$ is preferred. For example, Figure~\ref{fig:star-alt} gives two star partitioning results under 
different vertex ordering on the same graph. The top one has $\Gamma = 5$ while the bottom one has $\Gamma = 3$. Obviously, the bottom one with smaller $\Gamma$ is much more balanced.

\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{star-alt.eps}
\caption{Star partitioning with different vertex orderings.}
\label{fig:star-alt}
\end{figure}

@@

\begin{theorem}
\label{THM:SPM_LB}
Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be the value derived from a random vertex ordering. With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}
\begin{proof}
%\vspace{-0.5em}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
If $G_A$ is dense, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
\begin{theorem}
\label{THM:SPM_LB_INC}
Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
\end{theorem}
\begin{proof}
%\vspace{-0.5em}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
Hence, we can simply use object ID to determine the vertex ordering in our implementation.

@@

\begin{example}
Let $L = 2, K = 4$ and we follow the above example. $T_1$ is not a decomposable sequence
because one of its maximal $2$-connected subsequence (i.e., $T_1^B$) is not $2$-consecutive.
In contrast, $T_2$ is a decomposable sequence because the sequence itself is the maximal $2$-connected subsequence, which is also $2$-consecutive and with size  $\geq 4$.
\end{example}

@@

Our customized Apriori Enumerator is presented in Algorithm~\ref{algo:apriori_mining}. Initially, the edges (pairs of objects) in the star constitute the bottom level (Lines~\ref{code:init-start}-\ref{code:init-end}) and invalid candidates are excluded (Line~\ref{code:simp1}). An indicator \emph{level} is used to control the result size for candidate joins. During each iteration (Lines~\ref{code:level-start}-\ref{code:level-ends}), only candidates with object size equals to \emph{level} are generated (Line~\ref{code:join-start}). When two candidates $c_1$ and $c_2$ are joined, the new candidate becomes $c'=\langle c_1.O \cup c_2.O, c_1.T\cap c_2.T\rangle$ (Line~\ref{code:join}). To check the validity of the candidate, we calculate $\mathtt{sim}(c'.T)$. If its simplified sequence is empty, $c'$ is excluded from the next level (Line~\ref{code:simp2}). This ensures that all the candidates with $P.O\supseteq c'.O$ are pruned. If a candidate cannot generate any new candidate, then
it is directly reported (Lines~\ref{code:output1-start}-\ref{code:output1-end}).
To further improve the performance, we adopt the idea of \textit{forward closure}~\cite{wang2003closet+} and  aggressively check if the union of all the current candidates form a valid pattern (Lines~\ref{code:fc-checking-start}-\ref{code:fc-checking-end}). If yes, we can  terminate the algorithm early and output the results.

@@

Compared with TRPM, the SPARE framework does not rely on snapshot replication to guarantee correctness. In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
\begin{theorem}[Pattern Uniqueness]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
\end{theorem}
\begin{proof} 
%\vspace{-0.5em}
We prove by contradiction. Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set. Note that the center vertex of the star is associated with the minimum id. Let $o_i$ and $o_j$ be the center vertexes of the two partitions and we have $o_i=o_j$. However, $P_i$ and $P_j$ are from different stars, meaning their center vertexes are different (i.e., $o_i\neq o_j$), leading to a contradiction. 
%\vspace{-0.5em}
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}  
%\vspace{-0.5em}
See Appendix~\ref{apx:spm_correct}.
%\vspace{-0.5em}
\end{proof}
